Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-25 paper/Draft.tex
Efficiency test using FE table is in draft. Revision table remains to be added.

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\centering 
	\begin{tabular}{lll}

		\hline 
		& SCE & SPF        \\
		\hline 
		                                  &                             &             \\
	\end{tabular}
\end{table}

>>>>

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\centering 
\begin{tabular}{llll}
	\hline 
	& SPF CPI          & SPF PCE          & SCE            \\
	\hline 
	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
	\hline 
	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
	& (0.017)          & (0.061)          & (0.019)        \\
	\hline 
	N                                   & 4697             & 1208             & 67380          \\
	\hline 
	\multicolumn{4}{l}{Test2: FE Depends on past information}                                  \\
	\hline 
	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
	& (0.020)          & (0.061)          & NA             \\
	Constant                            & -0.655***        & -0.777***        & NA             \\
	& (0.060)          & (0.116)          & NA             \\
	\hline 
	N                                   & 3429             & 1208             & NA             \\
	$R^2$                 & 0.0721           & 0.118            & NA             \\
	\hline 
	\multicolumn{4}{l}{Test3: FE of non-overlapping forecast horizons are serially correlated} \\
	\hline 
	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
	& (0.020)          & (0.035)          & NA             \\
	Constant                            & 0.145***         & 0.275***         & NA             \\
	& (0.021)          & (0.035)          & NA             \\
	\hline 
	N                                   & 3356             & 1208             & NA             \\
	$R^2$                   & 0.00591          & 0.00264          & NA             \\
	\hline 
	\multicolumn{4}{l}{Test4: Overlapping FE are only weakly serially correlated}                          \\
	\hline 
	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
	& (0.025)          & (0.037)          & (0.021)        \\
	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
	& (0.027)          & (0.048)          & (0.046)        \\
	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
	& (0.025)          & (0.038)          & (0.045)        \\
	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
	& (0.019)          & (0.026)          & (0.097)        \\
	\hline 
	N                                   & 2536             & 1004             & 2836           \\
	$R^2$                & 0.439            & 0.552            & 0.232    \\
	\hline      
\end{tabular}
\end{table}
